Timely Object Recognition

### 2012-03-05 writeups/eccv12/technical.tex
yo

The final evaluation of a policy consists of the area under the performance vs. time curve.
Accordingly, we formulate per-action rewards such that their addition results in precisely this quantity.

Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
\begin{equation}\label{eq:advanced}
R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}^j)t_T^j}
\end{equation}
where $t_T^j$ is the time left until deadline at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.

\todo{explain the behavior}

@@

The feature representation of the belief state for a given action $a_i$ that corresponds to class $k$ is defined to be $[P(C_k), \, H(C_k), \, 1]$.

@@

With this policy, we gather $N$ recognition episodes.
We formulate a matrix $\Phi$ from the featurizations $\phi(b^j,a_i)$ that were seen in the gathered episodes, and a vector $y$ consisting of the individual rewards.
We then solve the system $\Phi \theta = y$.

>>>>

The final evaluation of a policy consists of the area under the performance vs. time curve (normalized by the total area).
Accordingly, we formulate per-action rewards such that their addition results in this quantity.

Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
\begin{equation}\label{eq:advanced}
R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}^j)t_T^j}
\end{equation}
where $t_T^j$ and $\text{ap}^j$ are the time left until deadline and the AP at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.

The reward is $1$ if the policy takes an action that obtains the maximum possible area under the curve at that point, and $0$ if no area under the curve is captured.

@@

The feature representation of the belief state for a given action $a_i$ that corresponds to class $k$ is defined to be
\begin{align}
[P(C_k), \, H(C_k), \, 1]
\end{align}

@@

With this policy, we run $N$ recognition episodes.
From the state-action samples gathered in running the episodes, we formulate a matrix $\Phi$ from the featurizations $\phi(b^j,a_i)$, and a vector $y$ consisting of the individual rewards $R(b^j,a_i)$.
We then solve the system $\Phi \theta = y$.
